### 2023-03-09 README.Rmd
Add citation information
add refinements before CRAN submission [no ci]

To reconstruct a historical R computational environment, this package assumes only the availability of source packages on CRAN. The reconstruction procedures have been tested in several vintage versions of R.

>>>>

To reconstruct a historical R computational environment, this package assumes only the availability of source packages online. The reconstruction procedures have been tested in several vintage versions of R.

Please cite this package as:

Chan CH, Schoch D (2023) rang: Reconstructing reproducible R computational environments. arXiv preprint:[2303.04758](https://doi.org/10.48550/arXiv.2303.04758)
